---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# criterioncollection <img src = "man/figures/criterion_hex.png" align = "right" height = "139" />

<!-- badges: start -->
[![R-CMD-check](https://github.com/arrismo/CriterionCollection/workflows/R-CMD-check/badge.svg)](https://github.com/arrismo/CriterionCollection/actions)
[![Lifecycle: experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://lifecycle.r-lib.org/articles/stages.html#experimental)
<!-- badges: end -->

## Overview

The [`criterioncollection`](https://github.com/arrismo/criterioncollection) R package is based around a data set of movies included in the Criterion Collection.

The Criterion Collection is a company dedicated to the restoration and distribution of films deemed to be important culturally, technically, or otherwise influential to the medium. Due to this mission, Criterion's associations have grown far beyond its primary purpose of distribution. A film being a part of the Criterion Collection is often seen as a badge of honor of sorts; the collection is sometimes viewed by cinephiles as a source of must-watch films.

The goal of this package is thus to make this data for movies widely seen as important and influential easy to view and analyze.

## Installation

The current version of criterioncollection can be installed from [GitHub](https://github.com/) with:

``` r
install.packages("remotes")
remotes::install_github("arrismo/criterioncollection")
```

## Loading and Usage

The current version of criterioncollection can be used primarily to access data on the Criterion Collection. The dataset, criterion, contains every item in the Criterion Collection and includes columns for `spine_number`, `year`, `country`, `title`, and `director`.

```{r example}
library(criterioncollection)
View(criterion)
?criterion
```

You can also view the boxsets dataset that contains the boxset title, individual movie title, and year released.
```{r}
View(boxsets)
?boxsets
```


You can use the following functions to find films by the director, spine, or film title. Each function outputs a data frame based on your input.

The `find_by_director()` function returns the data from the criterion data set for all movies in the Criterion Collection by a certain director.
```{r message=FALSE, paged.print=TRUE, warning = FALSE}
find_by_director("John Woo")
```

The `find_by_title()` and `find_by_spine()` functions return not only the data from the criterion data set, but also data from the **imdbapi** package. This will include more data for a single movie than the Criterion Collection supplies, such as its actors and its IMDb user rating.

```{r message=FALSE, paged.print=TRUE, warning = FALSE}
find_by_title("Grand Illusion")
```

Not all movies in the Criterion Collection have a spine number, but the `find_by_spine()` function can be helpful for the >1000 movies that do.

```{r message=FALSE, paged.print=TRUE, warning = FALSE}
find_by_spine("1")
```

The package also contains a dataset with only the boxsets and the movies in those boxsets. The contents of individual boxsets can be viewed using a similar function, find_boxset.
```{r message=FALSE, paged.print=TRUE}
find_boxset("The Koker Trilogy")
```


## References

* Criterion. _Shop All Films_. The Criterion Collection. https://www.criterion.com/shop/browse/list.

* Criterion. _Our Mission_. The Criterion Collection. https://www.criterion.com/about.

* Criterion. _Box Sets_. The Criterion Collection. 
https://www.criterion.com/shop/collection/380-box-sets

